Sparse Function-space Representation of Neural Networks

### 2023-05-30 workshop/main.tex
Edits

\begin{figure*}[t]
  \centering\scriptsize
  \setlength{\figurewidth}{.16\textwidth}
  \setlength{\figureheight}{\figurewidth}
  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
  %
  \begin{minipage}[t]{.13\textwidth}
    \raggedleft
    \pgfplotsset{ylabel=NLPD}
    \input{./fig/australian.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/breast_cancer.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/ionosphere.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/glass.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/vehicle.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/waveform.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/digits.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/satellite.tex}
  \end{minipage}\\[-1em]
  %
  % Legend  
  \definecolor{steelblue31119180}{RGB}{31,119,180}
  \definecolor{darkorange25512714}{RGB}{255,127,14}  
  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets (\cite{immer2021improving}, thin). Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean. Our \our converges fast for all cases.\looseness-1}
  \label{fig:uci}
  %\vspace*{-6pt}
\end{figure*}

>>>>

\begin{figure*}[t]
  \centering\scriptsize
  \setlength{\figurewidth}{.16\textwidth}
  \setlength{\figureheight}{\figurewidth}
  \pgfplotsset{axis on top,scale only axis,y tick label style={rotate=90}, x tick label style={font=\footnotesize},y tick label style={font=\footnotesize},title style={yshift=-4pt,font=\large}, y label style={font=\large},x label style={font=\large},grid=major, width=\figurewidth, height=\figureheight}
  \pgfplotsset{grid style={line width=.1pt, draw=gray!10,dashed}}
  \pgfplotsset{xlabel={$M$},ylabel style={yshift=-12pt}}  
  %
  \begin{minipage}[t]{.13\textwidth}
    \raggedleft
    \pgfplotsset{ylabel=NLPD}
    \input{./fig/australian.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/breast_cancer.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/ionosphere.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/glass.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/vehicle.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/waveform.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/digits.tex}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.12\textwidth}
    \raggedleft
    \input{./fig/satellite.tex}
  \end{minipage}\\[-1em]
  %
  % Legend  
  \definecolor{steelblue31119180}{RGB}{31,119,180}
  \definecolor{darkorange25512714}{RGB}{255,127,14}  
  \newcommand{\myline}[1]{\protect\tikz[baseline=-.5ex,line width=1.6pt]\protect\draw[draw=#1](0,0)--(1.2em,0);}
  \caption{Comparison of convergence in terms of number of inducing points $M$ in NLPD (mean over 10 seeds) on UCI classification tasks: \our (thick) vs.\ subsets \citep[][thin]{immer2021improving}. Orange lines (\myline{darkorange25512714}) use the GP mean, whereas blue lines (\myline{steelblue31119180}) the NN MAP estimate as mean. Our \our converges fast for all cases.\looseness-1}
  \label{fig:uci}
  %\vspace*{-6pt}
\end{figure*}
